---
title: "Barcelona RNAseq pilot project"
author: "daniel.lundin@lnu.se"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
knit: (function(fname, encoding) { rmarkdown::render(fname, encoding = encoding, output_file = sprintf('%s/%s.%s.pdf', dirname(fname), sub('.rmd', '', basename(fname)), format(Sys.time(), "%Y%m%d"))) })
output:
  pdf_document:
    fig_caption: yes
    fig_height: 9
    fig_width: 8
    number_sections: yes
    toc: yes
  html_document:
    toc: yes
---

```{r setup, echo=F}

knitr::opts_chunk$set(echo=F, fig.path='figures/')

```

```{r libraries, message=F}

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(kfigr))
suppressPackageStartupMessages(library(knitr))

```

```{r constants}

```

```{r functions}

```

This script requires the presence of a statistics file in the same directory as
the script. The file can be produced by a target in the `makefile.rootdir`, but
the actual content is produced by various targets in other library makefiles.

```{r read-data}

# Read the statistics file.
stats = read_tsv(
  'stats.long.tsv',
  col_types = cols(
    directory = col_character(), sample = col_character(), program = col_character(),
    outputtype = col_character(), filename = col_character(), count = col_integer()
  )
)

```

# Samples

These samples were included in the project (`r figr('samples', T, type='Table')`).

```{r samples}

samples = stats %>% filter(directory == 'samples') %>%
  select(sample, outputtype, count) %>%
  spread(outputtype, count) %>%
  mutate(diff = r1 - r2)

kable(
  samples,
  col.names = c('Sample', "5' read", "3' read", 'Difference'),
  caption = "Samples with counts per read mate. (The 'Difference' column should be all zeroes.)"
)

```

# Quality control

Write something...

After `sickle`, NN proportions of reads were retained (`figr('sickle', T, type='Table')).

```{r sickle}

sickle = stats %>% filter(directory == 'qc', program == 'pesickle') %>%
  select(sample, outputtype, count) %>%
  spread(outputtype, count) %>%
  inner_join(samples %>% select(sample, s.r1 = r1, s.r2 = r2), by='sample') %>%
  mutate(
    frem.r1 = r1 / s.r1,
    frem.r2 = r2 / s.r2
  )

kable(
  sickle %>% select(sample, r1, frem.r1, r2, frem.r2),
  col.names = c('Sample', "N. 5' reads", "Frac. remaining", "N. 3' reads", "Frac. remaining"),
  caption = "Samples after sickle in pe mode with default settings"
)

```
